Spatial Analysis

### 2021-06-29 Scripts/spatial_analisis.Rmd
misc
Area plot for multi spp

### Proportional change per species

@@

@@

total_fited <- historic_tif %>% 
  group_by(year,region) %>% 
  summarise(total_value = sum(value,na.rm=T),.groups = "drop")

# group by state
state_fit <- historic_tif %>% 
  group_by(state,year,region) %>% 
  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
  left_join(total_fited,
            by = c("year","region")) %>%
  mutate(percentage = state_value/total_value*100)

@@

>>>>

### Per species maps

@@

### Dynamic aggregated plot

@@

# group by state
state_fit <- historic_spp %>% 
  group_by(state,year,region) %>% 
  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
  left_join(total_fited,
            by = c("year","region")) %>%
  mutate(percentage = state_value/total_value*100)

@@

### Per Species Proportional change

# group by state
state_fit <- historic_spp %>% 
  group_by(state,year,region,spp) %>% 
  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
  left_join(total_fited,
            by = c("year","region","spp")) %>%
  mutate(percentage = state_value/total_value*100) %>% 
  group_by(state,region,spp) %>% 
  mutate(RMean = zoo::rollmean(x = percentage, 
                            10,
                            fill = NA,
                            na.rm=T)
    ) %>% 
  #Only show results for spring
  filter(str_detect(region,"Spring"),
         !is.na(RMean) # Remove NAs from rollmean
         ) %>%  
  left_join(state_lat)

# Plot me
ggplot(state_fit) +
  geom_area(
    aes(
      x = year,
      y = round(RMean),
      fill = order
      # fill = state
    )
  ) +
  ylab("Propotion (10 yrs running average)") +
  # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
  scale_fill_manual(
    "State",
    values = state_pallet,
    labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
  ) +
  my_ggtheme_p(leg_pos = "right") +
  theme(legend.key.width = unit(1,"line")) + 
  facet_wrap(~spp, ncol = 1, strip.position = "right") +
  ggsave(filename = "area_plot_avg_spp.jpg",
         plot = ggplot2::last_plot(),
         path = my_path("R","Figures"),
         width = 10,
         height = 12
  )
